### 2024-04-03 paper/paper-papaja.Rmd
ethics + wordcount

@@

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "5099"

@@

A case where mere exposure lead to a lower truth rating for a related statement (i.e., one implied to be false) would more clearly implicate an effect of mere exposure on beliefs. In our review of the literature, we find three reported experiments that offer preliminary evidence of this effect: Bacon [-@bacon1979] found that mere exposure to one statement ($P$) could lead to lower truth ratings for a new, contradictory statements($\neg P$) after a three-week delay. For instance, mere exposure to "crocodiles sleep with their eyes open" produced lower truth ratings for "crocodiles sleep with their eyes closed". Findings from an experiment by Garcia-Marques and colleagues [-@garcia-marques.etal2015] partially contradicted these results (using a slightly different exposure task), finding lower truth ratings for contradictory statements when participants were queried immediately, but finding the opposite pattern of results at the delay used by the original Bacon [-@bacon1979] study. A later series of experiments by Unkelbach and Rom [-@unkelbach.rom2017] replicated these new findings [@garcia-marques.etal2015], although the effects were not observed consistently in each experiment.

>>>>

  **Ethics Statement**: This research was conducted under the approval of the Institutional Review Board at Arizona State University, IRB protocol ID STUDY00013322. Informed consent was obtained from all participants.

@@

keywords          : "Illusory truth; Metacognition; Cognitive Psychology; Misinformation"
wordcount         : "5209"

@@

A case where mere exposure lead to a lower truth rating for a related statement (i.e., one implied to be false) would more clearly implicate an effect of mere exposure on beliefs. In our review of the literature, we find three reported studies that offer preliminary evidence of this effect: Bacon [-@bacon1979] found that mere exposure to one statement ($P$) could lead to lower truth ratings for a new, contradictory statements($\neg P$) after a three-week delay. For instance, mere exposure to "crocodiles sleep with their eyes open" produced lower truth ratings for "crocodiles sleep with their eyes closed". Findings from an experiment by Garcia-Marques and colleagues [-@garcia-marques.etal2015] partially contradicted these results (using a slightly different exposure task), finding lower truth ratings for contradictory statements when participants were queried immediately, but finding the opposite pattern of results at the delay used by the original Bacon [-@bacon1979] study. A later series of experiments by Unkelbach and Rom [-@unkelbach.rom2017] generally replicated the newer findings [@garcia-marques.etal2015], although the effects were not observed consistently in each experiment.
